Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators \thanks{ An abridged version of this manuscript was presented at the ABCM International Congress of Mechanical Engineering (COBEM \colorbox{yellow}{Completar... cidade etc}). }

### 2019-11-04 PaperMagneticProfiles_JBSMSE.tex
Complete list of symbols.

@@

\nomenclature[ak]{$K$}{permeability of the porous medium [\si{\meter\square}]}
\nomenclature[ac]{$c\ped{E}$}{Ergun constant of the porous medium}
\nomenclature[br]{$\rho$}{density [\si{\kg\per\cubic\meter}]}
\nomenclature[be]{$\varepsilon$}{porosity}
\nomenclature[av]{$V$}{velocity [\si{\meter\per\second}]}
\nomenclature[ap]{$P$}{pressure [\si{\pascal}]}
\nomenclature[bu]{$\mu$}{dynamic viscosity [\si{\pascal\second}]}

@@

\nomenclature[at]{$T$}{temperature [\si{\kelvin}]}
\nomenclature[at]{$t$}{time [\si{\second}]}
\nomenclature[az]{$z$}{axial coordinate [\si{\meter}]}

\nomenclature[aq]{$\rate{q}\ped{csg}$}{volumetric casing losses in the AMR model [\si{\watt\per\cubic\meter}]}
\nomenclature[ic]{csg}{regenerator casing}
\nomenclature[ah]{$\hheat$}{heat transfer coefficient [\si{\watt\per\meter\squared\per\kelvin}]}
\nomenclature[aa]{$A\ped{sf}$}{contact surface area between solid and fluid phases in the regenerator [\si{\meter^2}]}
\nomenclature[is]{sf}{relative to the heat transfer between solid and fluid phases in the regenerator}
\nomenclature[bb]{$\beta$}{surface area density [\si{\squared\meter\per\cubic\meter}]}
\nomenclature[ak]{$k\ap{eff}$}{effective thermal conductivity [\si{\watt\per\meter\per\kelvin}]}
\nomenclature[ad]{$D\ped{ld}$}{dispersion term in the AMR model [\si{\meter\square\per\second}]}
\nomenclature[af]{$f$}{cycle frequency [\si{\hertz}]}
\nomenclature[am]{$m$}{mass [\si{\kg}]}

@@

\nomenclature[ag]{$g(t)$}{dimensional waveform of the pressure gradient term in the fluid momentum equation}
\nomenclature[aA]{$A\ped{t}$}{amplitude of the pressure gradient waveform in the fluid momentum equation [\si{\meter\per\second\square}]}

@@

\nomenclature[vh]{HC}{hot cycle}
\nomenclature[vc]{CC}{cold cycle}

@@

\nomenclature[bt]{$\tau\ped{B}$}{blow duration [\si{\second}]}

@@

\nomenclature[am]{$M$}{magnetization field [\si{\ampere\per\meter}]}
\nomenclature[an]{$N\ped{D}$}{demagnetization tensor}

@@

\nomenclature[bt]{$\dtad$}{adiabatic temperature variation [\si{\kelvin}]}

@@

@@

\noindent such that there are four ramp periods in one full cycle. The ramp rate, \(\theta\ped{R}\), is:

@@

\nomenclature[azt]{$\tau\ped{R}$}{ramp period in the magnetic ramp profile [\si{\second}]}
\nomenclature[azt]{$\tau\ped{M}$}{magnetization period in the magnetic ramp  profile [\si{\second}]}
\nomenclature[azo]{$\theta\ped{R}$}{ramp rate in the magnetic ramp profile}

@@

\nomenclature[vr]{RM}{rectified cosine magnetic profile}

@@

The AMR model is solved for only one bed, but  assumes that the $N\ped{r}$ identical beds experience the same cycle. Thus, the extensive performance parameters are multiplied by that factor.

\nomenclature[an]{$N\ped{r}$}{number of regenerators}

@@

\begin{equation}
\label{eq:99}
\qc = N\ped{r}\frac{1}{\tau} \int_{\tau\ped{HB}} \mrate\ped{f}(t) c_{p,\mathrm{f}} \left( T\ped{C} -T\ped{f,CE} \right) \diffd{t}
\end{equation}

\nomenclature[vh]{HB}{hot blow}
\nomenclature[vc]{CE}{cold end}
\nomenclature[am]{$\mrate\ped{f}$}{mass flow rate [\si{\kg\per\second}]}
\nomenclature[vc]{C}{cold source}
\nomenclature[vc]{H}{hot source}

@@

\begin{equation}
\label{eq:103}
\wpump = N\ped{r}\frac{1}{\tau}\int_0^{\tau}\frac{\rate{m}\ped{f}}{\rho\ped{f}} \Delta P \diffd{t}
\end{equation}

\noindent where $\Delta P$ is the total pressure drop through the regenerator.

\nomenclature[awm]{$\wpump$}{pumping power [\si{\watt}]}
\nomenclature[awm]{$\wmag$}{magnetic power [\si{\watt}]}
\nomenclature[ap]{$\Delta P$}{pressure drop across one region [\si{\pascal}]}

@@

\noindent where $N\ped{v}$ is the number of valves, $\wvalven$ is the measured average nominal power for one normally-closed electronic valve and $\wrelayn$ is the nominal power for one controlling relay. The factor $\nicefrac{1}{2}$ is due to two valves being controlled by one relay.

\nomenclature[an]{$N\ped{v}$}{number of valves}
\nomenclature[aw]{$\wvalve$}{valve power [\si{\watt}]}
\nomenclature[aw]{$\wvalven$}{nominal power comsumption of one valve [\si{\watt}]}
\nomenclature[aw]{$\wrelayn$}{nominal power comsumption of one relay [\si{\watt}]}

@@

\begin{equation}
  \label{eq:198}
  \wvalve\,[\si{\watt}]= N\ped{v}\left(0.927 f\,[\si{\hertz}] + 1.023 F\ped{B} + 0.226 f\,[\si{\hertz}] F\ped{B} - 0.037\right)
\end{equation}

@@

\begin{equation}
  \label{eq:111}
  N\ped{v} = 2 N\ped{r}
\end{equation}

@@

\begin{table}[!ht]
  \centering
  \caption{AMR parameters kept fixed in the simulations with different magnetic profiles \colorbox{yellow}{Fabio, acho que as variaveis nao foram apresentadas na lista de simbolos}}
  \begin{tabular}{c|c}
\hline
\textbf{Parameter} & \textbf{Value}\\
\hline
   $D\ped{p}$ & \SI{0.5}{\mm}\\
$H\ped{r}$ & \SI{20}{\mm}\\
$W\ped{r}$ & \SI{25}{\mm}\\
$L\ped{r}$ & \SI{100}{\mm}\\
$N\ped{r}$ & 11 \\
$N\ped{v}$ & 22 \\
$T\ped{H}$ & \SI{298}{\kelvin}\\
$\tc$ & \SI{278}{\kelvin}\\
$\w\ped{NV}$ & \SI{4}{\watt}\\
$\w\ped{R}$ & \SI{0.36}{\watt}\\
\hline
  \end{tabular}

@@

\nomenclature[ad]{$D\ped{p}$}{particle diameter [\si{meter}]}

@@

\nomenclature[ia]{air}{air layer between magnets and regenerators}

@@

\begin{table}[!ht]
  \centering
  \begin{tabular}{c|c}
\hline
    \textbf{Parameter} & \textbf{Value} \\
\hline
$R\ped{o}$ & \SI{40}{\mm} \\
$W\ped{r}$ & \SI{30}{\mm} \\
$L\ped{r}$ & \SI{85}{\mm} \\
$N\ped{r}$ & \num{8} \\
$N\ped{v}$ & \num{16} \\
$f$ & \SI{1}{\hertz} \\
$T\ped{H}$ & \SI{305.5}{\kelvin} = \SI{32.5}{\celsius} \\
$\tc$ & \SI{270.5}{\kelvin} = \SI{-2.5}{\celsius} \\
$D\ped{p}$ & \SI{350}{\micro\meter} \\
$h\ped{csg}$ & \SI{0.5}{\mm} \\
$h\ped{air}$ & \SI{1}{\mm} \\
Casing material & Stainless steel \\
Number of layers & \num{3} \\
Curie temperatures of each layer & \num{273}, \num{283}, \SI{290}{\kelvin} \\ 
Length fractions of each layer & \num{20}, \num{20}, \SI{60}{\percent}\\
\hline
  \end{tabular}
  \caption{Fixed parameters for the AMR simulations used in this chapter}
  \label{tab:params-ramp}
\end{table}

>>>>

\nomenclature[ah]{$H\ped{reg}$}{regenerator height [\si{\meter}]}
\nomenclature[aw]{$W\ped{reg}$}{regenerator width [\si{\meter}]}
\nomenclature[al]{$L\ped{reg}$}{regenerator length [\si{\meter}]}
\nomenclature[ah]{$H$}{magnetic field [\si{\henry}]}

@@

\nomenclature[ak]{$K$}{permeability of the porous medium [\si{\meter\squared}]}
\nomenclature[ac]{$c\ped{E}$}{Ergun constant of the porous medium}
\nomenclature[br]{$\rho$}{density [\si{\kg\per\cubic\meter}]}
\nomenclature[be]{$\varepsilon$}{porosity}
\nomenclature[av]{$V$}{velocity [\si{\meter\per\second}]}
\nomenclature[ap]{$P$}{pressure [\si{\pascal}]}
\nomenclature[bu]{$\mu\ped{f}$}{fluid dynamic viscosity [\si{\pascal\second}]}

@@

\nomenclature[at]{$T$}{temperature [\si{\kelvin}]}
\nomenclature[at]{$t$}{time [\si{\second}]}
\nomenclature[ax]{$x,y,z$}{coordinate system variables [\si{\meter}]}
\nomenclature[ip]{$p$}{constant-pressure}

\nomenclature[aq]{$\rate{q}\ped{csg}$}{volumetric casing losses in the AMR model [\si{\watt\per\cubic\meter}]}
\nomenclature[ic]{csg}{regenerator casing}
\nomenclature[ah]{$\hheat$}{heat transfer coefficient [\si{\watt\per\meter\squared\per\kelvin}]}
\nomenclature[aa]{$A\ped{sf}$}{contact surface area between solid and fluid phases in the regenerator [\si{\meter^2}]}
\nomenclature[is]{sf}{relative to the heat transfer between solid and fluid phases in the regenerator}
\nomenclature[bb]{$\beta$}{surface area density [\si{\square\meter\per\cubic\meter}]}
\nomenclature[ak]{$k$}{thermal conductivity [\si{\watt\per\meter\per\kelvin}]}
\nomenclature[ad]{$D\ped{ld}$}{dispersion term in the AMR model [\si{\meter\square\per\second}]}
\nomenclature[af]{$f$}{cycle frequency [\si{\hertz}]}
\nomenclature[am]{$m$}{mass [\si{\kg}]}

@@

\nomenclature[ag]{$g(t)$}{dimensional waveform of the pressure gradient term in the fluid momentum equation}
\nomenclature[aA]{$A\ped{t}$}{amplitude of the pressure gradient waveform in the fluid momentum equation [\si{\meter\per\second\squared}]}

@@

\nomenclature[vh]{HC}{hot cycle}
\nomenclature[vc]{CC}{cold cycle}
\nomenclature[vc]{CB}{cold blow}
\nomenclature[bt]{$\tau\ped{0,CC}, \tau\ped{0,HC}$  }{time periods without fluid flow in the respective half-cycle (see list of Abbreviations) [\si{\second}]}

@@

\nomenclature[bt]{$\tau\ped{B}$}{blow duration [\si{\second}]}
\nomenclature[af]{$F\ped{B}$}{blow fraction}

@@

\nomenclature[am]{$M$}{magnetization field [\si{\henry}]}
\nomenclature[an]{$N\ped{D}$}{demagnetization tensor}
\nomenclature[ie]{eff}{effective}

@@

\nomenclature[at]{$\dtad$}{adiabatic temperature variation [\si{\kelvin}]}

@@

\nomenclature[ab]{$B$}{magnetic flux density [\si{\tesla}]}
\nomenclature[bu]{$\mu_0$}{magnetic permeability of free space [\si{\henry\per\meter}]}

@@

\noindent such that there are four ramp periods in one full cycle. The ramp rate, \(\tan \theta\ped{R}\), is:

@@

\nomenclature[bt]{$\tau\ped{R}$}{ramp period in the magnetic ramp profile [\si{\second}]}
\nomenclature[bt]{$\tau\ped{M}$}{magnetization period in the magnetic ramp  profile [\si{\second}]}
\nomenclature[bo]{$\tan \theta\ped{R}$}{ramp rate in the magnetic ramp profile [\si{\tesla\per\second}]}

@@

\nomenclature[vr]{RM}{ramp magnetic profile}

@@

The AMR model is solved for only one bed, but  assumes that the $N\ped{reg}$ identical beds experience the same cycle. Thus, the extensive performance parameters are multiplied by that factor.

\nomenclature[an]{$N\ped{reg}$}{number of regenerators}

@@

\begin{equation}
\label{eq:99}
\qc = N\ped{reg}\frac{1}{\tau} \int_{\tau\ped{HB}} \mrate\ped{f}(t) c_{p,\mathrm{f}} \left( T\ped{C} -T\ped{f,CE} \right) \diffd{t}
\end{equation}

\nomenclature[vh]{HB}{hot blow}
\nomenclature[vc]{CE}{cold end}
\nomenclature[am]{$\mrate\ped{f}$}{mass flow rate [\si{\kg\per\second}]}
\nomenclature[vc]{C}{cold source}
\nomenclature[vc]{H}{hot source}
\nomenclature[aq]{$\qc$}{cooling capacity [\si{\watt}]}

@@

\begin{equation}
\label{eq:103}
\wpump = N\ped{reg}\frac{1}{\tau}\int_0^{\tau}\frac{\rate{m}\ped{f}}{\rho\ped{f}} \Delta P \diffd{t}
\end{equation}

\noindent where $\Delta P$ is the total pressure drop through the regenerator (including one hot and one cold blow).

\nomenclature[awm]{$\wpump$}{pumping power [\si{\watt}]}
\nomenclature[awm]{$\wmag$}{magnetic power [\si{\watt}]}
\nomenclature[ap]{$\Delta P$}{total pressure drop across one regenerator [\si{\pascal}]}

@@

\noindent where $N\ped{valve}$ is the number of valves, $\wvalven$ is the measured average nominal power for one normally-closed electronic valve and $\wrelayn$ is the nominal power for one controlling relay. The factor $\nicefrac{1}{2}$ is due to two valves being controlled by one relay.

\nomenclature[an]{$N\ped{valve}$}{number of valves}
\nomenclature[aw]{$\wvalve$}{valve power [\si{\watt}]}
\nomenclature[aw]{$\wvalven$}{nominal power comsumption of one valve [\si{\watt}]}
\nomenclature[aw]{$\wrelayn$}{nominal power comsumption of one relay [\si{\watt}]}

@@

\begin{equation}
  \label{eq:198}
  \wvalve\,[\si{\watt}]= N\ped{valve}\left(0.927 f\,[\si{\hertz}] + 1.023 F\ped{B} + 0.226 f\,[\si{\hertz}] F\ped{B} - 0.037\right)
\end{equation}

@@

\begin{equation}
  \label{eq:111}
  N\ped{valve} = 2 N\ped{reg}
\end{equation}

@@

\begin{table}[!ht]
  \centering
  \caption{AMR parameters kept fixed in the simulations with different magnetic profiles}
  \begin{tabular}{c|c}
\hline
\textbf{Parameter} & \textbf{Value}\\
\hline
   $D\ped{p}$ & \SI{0.5}{\mm}\\
$H\ped{reg}$ & \SI{20}{\mm}\\
$W\ped{reg}$ & \SI{25}{\mm}\\
$L\ped{reg}$ & \SI{100}{\mm}\\
$N\ped{reg}$ & 11 \\
$N\ped{valve}$ & 22 \\
$T\ped{H}$ & \SI{298}{\kelvin}\\
$\tc$ & \SI{278}{\kelvin}\\
$\wvalven$ & \SI{4}{\watt}\\
$\wrelayn$ & \SI{0.36}{\watt}\\
\hline
  \end{tabular}

@@

\nomenclature[ad]{$D\ped{p}$}{particle diameter [\si{\meter}]}

@@

\nomenclature[ia]{air}{air layer between magnets and regenerators}
\nomenclature[ah]{$h$}{thickness [\si{\meter}]}

@@

\begin{table}[!ht]
  \centering
  \begin{tabular}{c|c}
\hline
    \textbf{Parameter} & \textbf{Value} \\
\hline
$W\ped{reg}$ & \SI{30}{\mm} \\
$L\ped{reg}$ & \SI{85}{\mm} \\
$N\ped{reg}$ & \num{8} \\
$N\ped{valve}$ & \num{16} \\
$f$ & \SI{1}{\hertz} \\
$T\ped{H}$ & \SI{305.5}{\kelvin} = \SI{32.5}{\celsius} \\
$\tc$ & \SI{270.5}{\kelvin} = \SI{-2.5}{\celsius} \\
$D\ped{p}$ & \SI{350}{\micro\meter} \\
$h\ped{csg}$ & \SI{0.5}{\mm} \\
$h\ped{air}$ & \SI{1}{\mm} \\
Casing material & Stainless steel \\
Number of layers & \num{3} \\
Curie temperatures of each layer & \num{273}, \num{283}, \SI{290}{\kelvin} \\ 
Length fractions of each layer & \num{20}, \num{20}, \SI{60}{\percent}\\
\hline
  \end{tabular}
  \caption{Fixed parameters for the AMR simulations used in this chapter}
  \label{tab:params-ramp}
\end{table}
